Exploration

### 2018-03-02 exploration.Rmd
finished seedbank

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pkgs <- c("fields", "sevcheck", "gbPopMod", "IPMpack", "tidyverse", "magrittr")
suppressMessages(invisible(lapply(pkgs, library, character.only=TRUE)))
theme_set(theme_bw())
source("code/fn_IPM.R"); source("code/fn_aux.R")
lc.df <- read_csv("data/landcover_5km.csv") %>% 
  filter(!is.na(bio1_mean))
```

@@

## Species description: Life history, characteristics, relevant attributes
The simulated species is fully described here. The object `sp_i` is a list containing elements for the global parameters, relationships with environmental variables, and demographic matrices that are applicable or potentially applicable for that modeling strategy. Parameters are abbreviated with the associated kernel component (e.g., `s_*` for survival, `g_*` for growth, etc) and the type of covariate (`*_z` for size, `*_x` for environmental covariates).
```{r sp_i}
subsamp <- NA
mean_abund <- 2000
regPlots <- F
ipmPlots <- F
n <- 100  # ncells in IPM matrix
if(is.na(subsamp)) { cells <- 1:n_distinct(lc.df$CellID)
} else { cells <- sample(1:n_distinct(lc.df$CellID), subsamp, replace=FALSE) }
n.cell <- length(cells)
n_i <- rpois(n.cell, mean_abund)
sp_i <- list(p=list(s_z=c(-1.75, .75), # b1 + b2*z
                    s_x=c(1, -.1, -.5, -.1, .05), # b1*x1 + ...
                    g_z=c(.2, 2, -0.1), # b1 + b2*z + b3*z^2
                    g_x=c(1, -.1, 1.5, -.1), #b1*x1 + ...
                    g_sig=1, # growth ~ N(E, g_sig)
                    fl_z=c(-1.5, .1, .1), # b1 + b2*z + b3*z^2 + b4*z^3
                    fl_x=c(1, -.01, -1, -.01, .2), # b1*x1 + ...
                    seed_z=c(2, 0.5, -.03), # b1 + b2*z + b2*z^2
                    seed_x=c(1, -.1, 1, -.1, .2), # b1*x1 + ...
                    rcr_z=c(1.5, 0.4), # N(mean=rcrt1, sd=rcrt2)
                    p_est=0.02, # p(establishment)
                    rcr_SB=0.2, # p(recruit from seedbank)
                    rcr_dir=0.6, # p(recruit directly)
                    s_SB=0.3 # p(survive in seedbank additional year)
                    ))
```

@@

## Simulation: IPM framework
```{r S}
########
## set up
########
# set up storage objects
p <- sp_i$p
IPMs <- Ps <- Fs <- array(0, dim=c(n+1, n+1, n.cell))
d <- vector("list", length=n.cell)
lambdas <- B_1 <- rep(NA, n.cell)
B <- rpois(n.cell, n_i)

@@

########
## loop through cells
########
for(i in 1:n.cell) {
  d[[i]] <- data.frame(size=runif(n=n_i[i], min=1, max=12))
  lo <- min(d[[i]]$size)*0.75
  hi <- max(d[[i]]$size)*1.25
  size.mx <- cbind(1, d[[i]]$size, d[[i]]$size^2, d[[i]]$size^3)

  #---- generate data
  ## survival
  E_surv <- antilogit(size.mx[,1:n_sz] %*% p$s_z + c(X_s[i,] %*% p$s_x))
  d[[i]]$surv <- rbinom(n_i[i], 1, E_surv)
  ## growth
  E_grow <- size.mx[,1:n_gz] %*% p$g_z + c(X_g[i,] %*% p$g_x)
  d[[i]]$sizeNext <- rnorm(n_i[i], E_grow, p$g_sig)
  d[[i]]$sizeNext <- ifelse(d[[i]]$surv, d[[i]]$sizeNext, NA)
  ## flowering 
  E_fl <- antilogit(size.mx[,1:n_flz] %*% p$fl_z + c(X_fl[i,] %*% p$fl_x))
  d[[i]]$fl <- rbinom(n_i[i], 1, E_fl)
  ## seed production
  E_seed <- d[[i]]$fl * 
    exp(size.mx[,1:n_seedz] %*% p$seed_z + c(X_seed[i,] %*% p$seed_x))
  d[[i]]$seed <- rpois(n_i[i], E_seed)
  d[[i]]$fl <- ifelse(d[[i]]$surv, d[[i]]$fl, NA)
  d[[i]]$seed <- ifelse(d[[i]]$fl==1, d[[i]]$seed, NA)
  ## seed bank
  B_1[i] <- B[i] * p$s_SB * (1 - p$rcr_SB) + 
    sum(d[[i]]$seed, na.rm=TRUE) * (1 - p$rcr_dir) * p$s_SB
  ## recruits
  rcrt.n <- max((sum(d[[i]]$seed, na.rm=TRUE) * p$rcr_dir * p$p_est +
                   B[i] * p$rcr_SB * p$p_est), 
                2) # need ≥ 2 for IPMpack estimate of rcr_z'_mn, rcr_z'_sd
  rcrt.i <- (n_i[i]+1):(n_i[i]+rcrt.n)
  d[[i]][rcrt.i,] <- NA
  d[[i]]$sizeNext[rcrt.i] <- rnorm(rcrt.n, p$rcr_z[1], p$rcr_z[2])

  #---- Truth: use assigned slopes to fill IPM matrix
  b <- lo + c(0:n)*(hi - lo)/n  # boundary points
  y <- 0.5*(b[1:n] + b[2:(n+1)])  # mesh points
  h <- y[2] - y[1]  # step size
  z.i <- 2:(n+1)  # continuous stage matrix indices
  ### growth and survival
  G.mx <- h*outer(y, y, calc_grow, p=p, n_gz=n_gz, X.g=X_g[i,])
  S.v <- calc_surv(y, p=p, n_sz=n_sz, X.s=X_s[i,])
  ### Fix eviction of individuals below/above size limits
  for(k in 1:(n/2)) G.mx[1,k] <- G.mx[1,k] + 1 - sum(G.mx[,k])
  for(k in (n/2+1):n) G.mx[n,k] <- G.mx[n,k] + 1 - sum(G.mx[,k])
  ### fill P, F, and K
  for(k in z.i) Ps[k,z.i,i] <- G.mx[k-1,]*S.v
  Ps[1,1,i] <- calc_staySB(p)
  Fs[z.i,z.i,i] <- h*outer(y, y, calc_rcrDir, p=p, n_seedz=n_seedz,
                             n_flz=n_flz, X.seed=X_seed[i,], X.fl=X_fl[i,])
  Fs[1,z.i,i] <- calc_addSB(y, p=p, n_seedz=n_seedz, n_flz=n_flz, 
                            X.seed=X_seed[i,], X.fl=X_fl[i,])
  Fs[z.i,1,i] <- calc_rcrSB(y, p)
  IPMs[,,i] <- Ps[,,i] + Fs[,,i]

  #---- progress
  if(i %% 100 == 0) cat("Finished cell", i, "\n")
}
lam.df <- env.df
lam.df$lambda <- apply(IPMs, 3, function(x) Re(eigen(x)$values[1]))
ggplot(lam.df, aes(x=x, y=y, fill=log(lambda))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
par(mfrow=c(2,2))
plot(log(lambda) ~ temp, data=lam.df); abline(h=0, col="red", lty=2)
plot(log(lambda) ~ prec, data=lam.df); abline(h=0, col="red", lty=2)
plot(log(lambda) ~ pOpn, data=lam.df); abline(h=0, col="red", lty=2)
plot(density(log(lam.df$lambda))); abline(v=0, col="red", lty=2)

# Plots
if(regPlots) {
  par(mfrow=c(3,2), mar=c(4,4,2,1))
  xx <- tibble(size=seq(lo, hi, length.out=100), size2=size^2, size3=size^3)
  mx <- cbind(1, as.matrix(xx))
  xxx <- seq(0, hi*.5, length.out=100)
  for(i in 1:n.cell) {
    z.t <- d[[i]][!is.na(d[[i]]$size),]; main.i <- paste("Cell", i)
    w1 <- Re(eigen(IPMs[,,i])$vectors[,1])[-1]; stable.dist1 <- w1/sum(w1)
    rcrt.z <- d[[i]]$sizeNext[is.na(d[[i]]$size) & !is.na(d[[i]]$sizeNext)]
    plot(surv~size, data=z.t, ylim=c(0,1), pch=20, col=rgb(0,0,0,0.2),
         main=paste("Surv:", main.i), xlab="Size (t)", ylab="P(surv to t+1)")
      lines(mx[,2], antilogit(mx[,1:n_sz]%*%p$s_z + c(X_s[i,]%*%p$s_x)), col=2)
    plot(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,0.2), 
         main=paste("Growth:", main.i), xlab="Size (t)", ylab="Size (t+1)")
      lines(mx[,2], mx[,1:n_gz]%*%p$g_z + c(X_g[i,]%*%p$g_x), col=2)
      abline(a=0, b=1, lty=2)
    plot(fl~size, data=z.t, pch=20, ylim=c(0,1), col=rgb(0,0,0,0.2),
         main=paste("P(Flower):", main.i), xlab="Size (t)", ylab="P(flower)")
      lines(mx[,2], antilogit(mx[,1:n_flz]%*%p$fl_z + c(X_fl[i,]%*%p$fl_x)),
            col=2)
    plot(seed~size, data=z.t, pch=23-z.t$fl*3, col=rgb(0,0,0,0.2), 
         main=paste("nSeeds:", main.i), xlab="Size (t)", ylab="Number of seeds")
      lines(mx[,2], exp(mx[,1:n_seedz]%*%p$seed_z + c(X_seed[i,]%*%p$seed_x)),
            col=2)
    plot(y, stable.dist1, ylab="", type="l", col=2, 
         main=paste("Stable size distribution:", main.i), xlab="Size (t)")
    hist(d[[i]]$sizeNext[is.na(d[[i]]$size)], col="grey", freq=FALSE, 
         main=paste("Recruit sizes:", main.i), xlab="Recruit size (t+1)")
      lines(xxx, dnorm(xxx, p$rcr_z[1], p$rcr_z[2]), col="red", lwd=2)
  }
}
if(ipmPlots) {
  par(mfrow=c(2,2), mar=c(4,4,2,1))
  x <- c(0, y)
  for(i in 1:n.cell) {
    z.t <- d[[i]][!is.na(d[[i]]$size),]; main.i <- paste("Cell", i)
    z.t$y <- y[findInterval(z.t$size, y, all.inside=TRUE)]
    totSeeds <- group_by(z.t, y) %>% summarise(seed=sum(seed, na.rm=TRUE))
    image.plot(x, x, t(Ps[,,i]), main=paste("P matrix:", main.i), 
               xlab="Size (t)", ylab="Size (t+1)")
      points(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,1/(n_i[i]^.25)))
      abline(a=0, b=1, col="white", lty=2)
    image.plot(x, x, t(Fs[,,i]), main=paste("F matrix:", main.i), 
               xlab="Size (t)", ylab="Size (t+1)")
      points(totSeeds$y, totSeeds$seed/max(totSeeds$seed)*hi*.9)
    image.plot(x, x, t(sens(IPMs[,,i])), main=paste("Sensitivity:", main.i), 
               xlab="Size (t)", ylab="Size (t+1)")
    image.plot(x, x, t(elas(IPMs[,,i])), main=paste("Elasticity:", main.i),
               xlab="Size (t)", ylab="Size (t+1)")
  }
}
```

@@

  if(regPlots) {
    par(mfrow=c(3,2), mar=c(4,4,2,1))
    xx <- tibble(size=seq(lo, hi, length.out=100), size2=size^2, size3=size^3)
    plot(surv~size, data=d[[i]], ylim=c(0,1), pch=20, col=rgb(0,0,0,0.2),
         main=paste("Surv:", main.i), xlab="Size (t)", ylab="P(surv to t+1)")
      points(z.t$size, E_surv, cex=0.2, col="red")
      # lines(xx$size, predict(so@fit, xx, type="response"), col="blue")
    plot(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,0.2), 
         main=paste("Growth:", main.i), xlab="Size (t)", ylab="Size (t+1)")
      points(z.t$size, E_grow, cex=0.2, col="red")
      # lines(xx$size, predict(go@fit, xx, type="response"), col="blue")
      abline(a=0, b=1, lty=2)
    plot(fl~size, data=z.t, pch=20, ylim=c(0,1), col=rgb(0,0,0,0.2),
         main=paste("P(Flower):", main.i), xlab="Size (t)", ylab="P(flower)")
      points(z.t$size, E_fl, cex=0.2, col="red")
      # lines(xx$size, predict(fo@fitFec[[1]], xx, type="response"), col="blue")
    plot(seed~size, data=z.t, pch=23-z.t$fl*3, col=rgb(0,0,0,0.2), 
         main=paste("nSeeds:", main.i), xlab="Size (t)", ylab="Number of seeds")
      points(z.t$size, E_seed, cex=0.2, col="red")
      # lines(xx$size, predict(fo@fitFec[[2]], xx, type="response"), col="blue")
    w1 <- Re(eigen(IPMs[,,i])$vectors[,1])[-1]; stable.dist1 <- w1/sum(w1)
    # w2 <- Re(eigen(IPM2)$vectors[,1])[-1]; stable.dist2 <- w2/sum(w2)
    yl <- range(stable.dist1)#range(c(stable.dist1, stable.dist2))
    plot(y, stable.dist1, ylab="", type="l", lwd=2, col="red", ylim=yl,
         main=paste("Stable size distribution:", main.i), xlab="Size (t)")
    # lines(y, stable.dist2, col="blue")
    hist(d[[i]]$sizeNext[rcrt.i], main=paste("Recruit sizes:", main.i), 
         xlab="Recruit size (t+1)", col="grey", freq=FALSE)
      xxx <- seq(0, hi*.5, length.out=100)
      rcrt.z <- d[[i]]$sizeNext[is.na(d[[i]]$size) & !is.na(d[[i]]$sizeNext)]
      lines(xxx, dnorm(xxx, p$rcr_z[1], p$rcr_z[2]), col="red", lwd=2)
      # lines(xxx, dnorm(xxx, mean(rcrt.z), sd(rcrt.z)), col="blue")
  }
}

>>>>

```{r setup, include=F}
knitr::opts_chunk$set(echo = T)
pkgs <- c("fields", "sevcheck", "gbPopMod", "IPMpack", "tidyverse", "magrittr")
suppressMessages(invisible(lapply(pkgs, library, character.only=T)))
theme_set(theme_bw())
source("code/fn_IPM.R"); source("code/fn_aux.R")
lc.df <- read_csv("data/landcover_5km.csv") %>% 
  filter(!is.na(bio1_mean))
```

@@

## Species description: Life history, characteristics, relevant attributes
The simulated species is fully described here. The object `sp_i` is a list containing elements for the global parameters, relationships with environmental variables, and demographic matrices that are applicable or potentially applicable for that modeling strategy. Parameters are abbreviated with the associated kernel component (e.g., `s_*` for survival, `g_*` for growth, etc) and the type of covariate (`*_z` for size, `*_x` for environmental covariates).
```{r sp_i}
subsamp <- 500
mean_abund <- 2000
regPlots <- F
ipmPlots <- F
z.rng <- c(1, 12)
n <- 100  # ncells in IPM matrix
if(is.na(subsamp)) { cells <- 1:n_distinct(lc.df$CellID)
} else { cells <- sample(1:n_distinct(lc.df$CellID), subsamp, replace=F) }
n.cell <- length(cells)
n_i <- rpois(n.cell, mean_abund)
sp_i <- list(p=list(s_z=c(-1.75, .75), # b1 + b2*z
                    s_x=c(1, -.1, -.5, -.1, .05, -2, -.4, -.4), # b1*x1 + ...
                    g_z=c(.2, 2, -0.1), # b1 + b2*z + b3*z^2
                    g_x=c(1, -.1, 1.5, -.1), #b1*x1 + ...
                    g_sig=1, # growth ~ N(E, g_sig)
                    fl_z=c(-1.5, .1, .1), # b1 + b2*z + b3*z^2 + b4*z^3
                    fl_x=c(1, -.01, -1, -.01, .2, .2), # b1*x1 + ...
                    seed_z=c(2, 0.5, -.03), # b1 + b2*z + b2*z^2
                    seed_x=c(1, -.1, 1, -.1, .2), # b1*x1 + ...
                    rcr_z=c(1.5, 0.4), # N(mean=rcrt1, sd=rcrt2)
                    p_est=0.02, # p(establishment)
                    rcr_SB=0.2, # p(recruit from seedbank)
                    rcr_dir=0.6, # p(recruit directly)
                    s_SB=0.3 # p(survive in seedbank additional year)
                    ))
```

@@

## Simulation: IPM framework
```{r S}
########
## set up
########
# set up storage & IPM matrix objects
p <- sp_i$p
setup_IPM_matrix(n, z.rng, buffer=0.25, discrete=1)
IPMs <- Ps <- Fs <- array(0, dim=c(n+1, n+1, n.cell))
d <- vector("list", length=n.cell)
B <- rpois(n.cell, n_i)
B_1 <- rep(NA, n.cell)

@@

########
## loop through cells
########
for(i in 1:n.cell) {
  d[[i]] <- data.frame(size=runif(n=n_i[i], min=z.rng[1], max=z.rng[2]))
  size.mx <- cbind(1, d[[i]]$size, d[[i]]$size^2, d[[i]]$size^3)

  #---- Truth: use assigned slopes to fill IPM matrix
  ### growth and survival
  G.mx <- h*outer(y, y, calc_grow, p=p, n_gz=n_gz, X.g=X_g[i,])
  S.v <- calc_surv(y, p=p, n_sz=n_sz, X.s=X_s[i,])
  ### Fix eviction of individuals below/above size limits
  for(k in 1:(n/2)) G.mx[1,k] <- G.mx[1,k] + 1 - sum(G.mx[,k])
  for(k in (n/2+1):n) G.mx[n,k] <- G.mx[n,k] + 1 - sum(G.mx[,k])
  ### fill P and F matrices
  for(k in z.i) Ps[k,z.i,i] <- G.mx[k-1,]*S.v
  Ps[1,1,i] <- calc_staySB(p)
  Fs[z.i,z.i,i] <- h*outer(y, y, calc_rcrDir, p=p, n_seedz=n_seedz,
                             n_flz=n_flz, X.seed=X_seed[i,], X.fl=X_fl[i,])
  Fs[1,z.i,i] <- calc_addSB(y, p=p, n_seedz=n_seedz, n_flz=n_flz, 
                            X.seed=X_seed[i,], X.fl=X_fl[i,])
  Fs[z.i,1,i] <- calc_rcrSB(y, p)

  #---- generate data
  ## survival
  E_surv <- antilogit(size.mx[,1:n_sz] %*% p$s_z + c(X_s[i,] %*% p$s_x))
  d[[i]]$surv <- rbinom(n_i[i], 1, E_surv)
  ## growth
  E_grow <- size.mx[,1:n_gz] %*% p$g_z + c(X_g[i,] %*% p$g_x)
  d[[i]]$sizeNext <- rnorm(n_i[i], E_grow, p$g_sig)
  d[[i]]$sizeNext <- ifelse(d[[i]]$surv, d[[i]]$sizeNext, NA)
  ## flowering 
  E_fl <- antilogit(size.mx[,1:n_flz] %*% p$fl_z + c(X_fl[i,] %*% p$fl_x))
  d[[i]]$fl <- rbinom(n_i[i], 1, E_fl)
  ## seed production
  E_seed <- d[[i]]$fl * 
    exp(size.mx[,1:n_seedz] %*% p$seed_z + c(X_seed[i,] %*% p$seed_x))
  d[[i]]$seed <- rpois(n_i[i], E_seed)
  d[[i]]$fl <- ifelse(d[[i]]$surv, d[[i]]$fl, NA)
  d[[i]]$seed <- ifelse(d[[i]]$fl==1, d[[i]]$seed, NA)
  ## seed bank
  B_1[i] <- B[i] * p$s_SB * (1 - p$rcr_SB) + 
    sum(d[[i]]$seed, na.rm=T) * (1 - p$rcr_dir) * p$s_SB
  ## recruits
  rcrt.n <- max((sum(d[[i]]$seed, na.rm=T) * p$rcr_dir * p$p_est +
                   B[i] * p$rcr_SB * p$p_est), 2) # ≥ 2 for IPMpack sd(rcr_z')
  rcrt.i <- (n_i[i]+1):(n_i[i]+rcrt.n)
  d[[i]][rcrt.i,] <- NA
  d[[i]]$sizeNext[rcrt.i] <- rnorm(rcrt.n, p$rcr_z[1], p$rcr_z[2])
}
IPMs <- Ps + Fs
lam.df <- env.df
lam.df$lambda <- apply(IPMs, 3, function(x) Re(eigen(x)$values[1]))

########
## plots
########
ggplot(lam.df, aes(x=x, y=y, fill=log(lambda))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=x, y=y, fill=lambda>1)) + geom_tile()
par(mfrow=c(2,2))
plot(log(lambda) ~ temp, data=lam.df); abline(h=0, col="red", lty=2)
plot(log(lambda) ~ prec, data=lam.df); abline(h=0, col="red", lty=2)
plot(log(lambda) ~ pOth, data=lam.df); abline(h=0, col="red", lty=2)
plot(density(log(lam.df$lambda))); abline(v=0, col="red", lty=2)

if(regPlots) {
  par(mfrow=c(3,2), mar=c(4,4,2,1))
  xx <- tibble(size=seq(lo, hi, length.out=100), size2=size^2, size3=size^3)
  mx <- cbind(1, as.matrix(xx))
  xxx <- seq(0, hi*.5, length.out=100)
  for(i in 1:n.cell) {
    z.t <- d[[i]][!is.na(d[[i]]$size),]; main.i <- paste("Cell", i)
    w1 <- Re(eigen(IPMs[,,i])$vectors[,1])[-1]; stable.dist1 <- w1/sum(w1)
    rcrt.z <- d[[i]]$sizeNext[is.na(d[[i]]$size) & !is.na(d[[i]]$sizeNext)]
    plot(surv~size, data=z.t, ylim=c(0,1), pch=20, col=rgb(0,0,0,0.2),
         main=paste("Surv:", main.i), xlab="Size (t)", ylab="P(surv to t+1)")
      lines(mx[,2], antilogit(mx[,1:n_sz]%*%p$s_z + c(X_s[i,]%*%p$s_x)), col=2)
    plot(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,0.2), 
         main=paste("Growth:", main.i), xlab="Size (t)", ylab="Size (t+1)")
      lines(mx[,2], mx[,1:n_gz]%*%p$g_z + c(X_g[i,]%*%p$g_x), col=2)
      abline(a=0, b=1, lty=2)
    plot(fl~size, data=z.t, pch=20, ylim=c(0,1), col=rgb(0,0,0,0.2),
         main=paste("P(Flower):", main.i), xlab="Size (t)", ylab="P(flower)")
      lines(mx[,2], antilogit(mx[,1:n_flz]%*%p$fl_z + c(X_fl[i,]%*%p$fl_x)),
            col=2)
    plot(seed~size, data=z.t, pch=23-z.t$fl*3, col=rgb(0,0,0,0.2), 
         main=paste("nSeeds:", main.i), xlab="Size (t)", ylab="Number of seeds")
      lines(mx[,2], exp(mx[,1:n_seedz]%*%p$seed_z + c(X_seed[i,]%*%p$seed_x)),
            col=2)
    plot(y, stable.dist1, ylab="", type="l", col=2, 
         main=paste("Stable size distribution:", main.i), xlab="Size (t)")
    hist(d[[i]]$sizeNext[is.na(d[[i]]$size)], col="grey", freq=F, 
         main=paste("Recruit sizes:", main.i), xlab="Recruit size (t+1)")
      lines(xxx, dnorm(xxx, p$rcr_z[1], p$rcr_z[2]), col="red", lwd=2)
  }
}
if(ipmPlots) {
  par(mfrow=c(2,2), mar=c(4,4,2,1))
  x <- c(0, y)
  for(i in 1:n.cell) {
    z.t <- d[[i]][!is.na(d[[i]]$size),]; main.i <- paste("Cell", i)
    z.t$y <- y[findInterval(z.t$size, y, all.inside=T)]
    totSeeds <- group_by(z.t, y) %>% summarise(seed=sum(seed, na.rm=T))
    image.plot(x, x, t(Ps[,,i]), main=paste("P matrix:", main.i), 
               xlab="Size (t)", ylab="Size (t+1)")
      points(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,1/(n_i[i]^.25)))
      abline(a=0, b=1, col="white", lty=2)
    image.plot(x, x, t(Fs[,,i]), main=paste("F matrix:", main.i), 
               xlab="Size (t)", ylab="Size (t+1)")
      points(totSeeds$y, totSeeds$seed/max(totSeeds$seed)*hi*.9)
    image.plot(x, x, t(sens(IPMs[,,i])), main=paste("Sensitivity:", main.i), 
               xlab="Size (t)", ylab="Size (t+1)")
    image.plot(x, x, t(elas(IPMs[,,i])), main=paste("Elasticity:", main.i),
               xlab="Size (t)", ylab="Size (t+1)")
  }
}
```

@@

  if(regPlots) {
    par(mfrow=c(3,2), mar=c(4,4,2,1))
    xx <- tibble(size=seq(lo, hi, length.out=100), size2=size^2, size3=size^3)
    plot(surv~size, data=d[[i]], ylim=c(0,1), pch=20, col=rgb(0,0,0,0.2),
         main=paste("Surv:", main.i), xlab="Size (t)", ylab="P(surv to t+1)")
      points(z.t$size, E_surv, cex=0.2, col="red")
      # lines(xx$size, predict(so@fit, xx, type="response"), col="blue")
    plot(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,0.2), 
         main=paste("Growth:", main.i), xlab="Size (t)", ylab="Size (t+1)")
      points(z.t$size, E_grow, cex=0.2, col="red")
      # lines(xx$size, predict(go@fit, xx, type="response"), col="blue")
      abline(a=0, b=1, lty=2)
    plot(fl~size, data=z.t, pch=20, ylim=c(0,1), col=rgb(0,0,0,0.2),
         main=paste("P(Flower):", main.i), xlab="Size (t)", ylab="P(flower)")
      points(z.t$size, E_fl, cex=0.2, col="red")
      # lines(xx$size, predict(fo@fitFec[[1]], xx, type="response"), col="blue")
    plot(seed~size, data=z.t, pch=23-z.t$fl*3, col=rgb(0,0,0,0.2), 
         main=paste("nSeeds:", main.i), xlab="Size (t)", ylab="Number of seeds")
      points(z.t$size, E_seed, cex=0.2, col="red")
      # lines(xx$size, predict(fo@fitFec[[2]], xx, type="response"), col="blue")
    w1 <- Re(eigen(IPMs[,,i])$vectors[,1])[-1]; stable.dist1 <- w1/sum(w1)
    # w2 <- Re(eigen(IPM2)$vectors[,1])[-1]; stable.dist2 <- w2/sum(w2)
    yl <- range(stable.dist1)#range(c(stable.dist1, stable.dist2))
    plot(y, stable.dist1, ylab="", type="l", lwd=2, col="red", ylim=yl,
         main=paste("Stable size distribution:", main.i), xlab="Size (t)")
    # lines(y, stable.dist2, col="blue")
    hist(d[[i]]$sizeNext[rcrt.i], main=paste("Recruit sizes:", main.i), 
         xlab="Recruit size (t+1)", col="grey", freq=F)
      xxx <- seq(0, hi*.5, length.out=100)
      rcrt.z <- d[[i]]$sizeNext[is.na(d[[i]]$size) & !is.na(d[[i]]$sizeNext)]
      lines(xxx, dnorm(xxx, p$rcr_z[1], p$rcr_z[2]), col="red", lwd=2)
      # lines(xxx, dnorm(xxx, mean(rcrt.z), sd(rcrt.z)), col="blue")
  }
}
